{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-10-09 documents/acknowledgement.tex
Protein charges processed

This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic nation-state supported tools like Paraview and Chimera to poorly-compensated but equally invaluable scripts like zonca. A special thanks to the dedicated authors that develop and maintain these tools.

@@

GThanks to L.H. for wisdom regarding this project; and H.P. and ice9 for tolerating midnight ramblings and M.Q. for the hug.

>>>>

This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic nation-state supported tools like Paraview to poorly-compensated but equally invaluable scripts like zonca. A special thanks to the dedicated authors that develop and maintain these tools.

@@

Prof. Griffiths and Dr. Brovko at UGuelph, Dr. Anany at the Guelph Research and Development Centre for tips on the Beta-Glo assay.

Thanks to L.H. for wisdom regarding this project; Profs David and Taylor (among others) at YorkU for being super nice, and H.P. and ice9 for tolerating midnight ramblings.
